FoRTE baseline

### 2019-05-08 analysis/paper/paper.Rmd
Use CSV parameter table in paper and elsewhere

- **Early successional hardwood**
    - _Betula papyrifera_ (white/paper birch)
    - _Populus grandidentata_ (bigtooth aspen)
    - ?? _Populus tremuloides_ (trembling aspen)
    - ?? _Prunus pensylvatica_ (fire cherry)
- **Mid successional hardwood**
    - _Quercus rubra_ (red oak)
    - _Acer rubrum_ (red maple)
    - ?? _Betula alleghaniensis_ (yellow birch)
    - ?? _Tilia americana_ (basswood)
    - ?? _Fraxinus americana_ (white ash)
- **Late successional hardwood**
    - _Acer saccharum_ (sugar maple)
    - _Fagus grandifolia_ (American beech)
    - ?? _Ostyra virginiana_ (hop-hornbeam)
    - ?? _Acer pensylvaticum_ (striped maple)
- **Pine**
    - _Pinus strobus_ (white pine)
    - ?? _Pinus resinosa_

| Parameter name (ED name)            | Description                                          | Unit                          |
|-------------------------------------|------------------------------------------------------|-------------------------------|
| `c2n_fineroot`                      | C:N ratio in fine roots                              | unitless (mass ratio)         |
| `c2n_leaf`                          | C:N ratio in leaves                                  | unitless (mass ratio)         |
| `f_labile`                          | Fraction of litter that goes to labile (fast) C pool | unitless (0-1)                |
| `fineroot2leaf` (`q`)               | Ratio of fine root to leaf biomass                   | unitless (mass ratio)         |
| `growth_resp_factor`                | Fraction of daily C gain lost to growth respiration  | unitless (0-1)                |
| `leaf_turnover_rate`                | Temperature dependent rate of leaf loss              | year^-1^                      |
| `Rd0`                               | Leaf dark respiration at 15 °C                       | ???                           |
| `dark_respiration_factor` #         | Ratio of leaf respiration to Vcmax                   | ???                           |
| `root_respiration_rate` (`_factor`) | Root respiration rate at 15 °C                       | μmol CO~2~ (kg fine root)^-1^ |
| `root_turnover_rate`                | Temperature dependent rate of fine root loss         | year^-1^                      |
| `leaf_width`                        | Mean leaf width (for boundary layer conductance)     | m                             |
| `mort2`                             | C balance ratio at which mortality rapidly increases | unitless (mass ratio)         |
| `nonlocal_dispersal`                | "Proportion of dispersal that is global"             | unitless (0-1)                |
| `quantum_efficiency`                | Farquhar model parameter (TODO)                      | mol CO~2~ (mol photons)^-1^   |
| `r_fract`                           | Fraction of C storage to seed reproduction           | unitless                      |
| `SLA`                               | Specific leaf area                                   | m^2^ kg^-1^ C                 |
| `seedling_mortality`                | Proportion of seed that dies and goes to litter pool | unitless (0-1)                |
| `stomatal_slope`                    | Slope between _A_ and stomatal conductance (Leuning) | unitless                      |
| `Vcmax` (`Vm0`)                     | Maximum rate of CO~2~ carboxylation at 15 °C         | μmol m^-2^ s^-1^              |
| `Vm_low_temp`                       | Minimum temperature for photosynthesis               | °C                            |
| `water_conductance`                 | "Water availability factor"                          | m^-2^ a^-1^ (kg C root)^-1^   |

Table: Parameter descriptions. For additional information, see the [ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters).

>>>>

- **Early successional hardwood**
    - _Betula papyrifera_ (white/paper birch)
    - _Populus grandidentata_ (bigtooth aspen)
    - _Populus tremuloides_ (trembling aspen)
- **Mid successional hardwood**
    - _Quercus rubra_ (red oak)
    - _Acer rubrum_ (red maple)
    - _Acer pensylvaticum_ (striped maple)
- **Late successional hardwood**
    - _Acer saccharum_ (sugar maple)
    - _Fagus grandifolia_ (American beech)
- **Pine**
    - _Pinus strobus_ (white pine)
- _Omitted candidates_
    - Early hardwood
        - _Prunus pensylvatica_ (fire cherry)
    - Mid hardwood
        - _Betula alleghaniensis_ (yellow birch)
        - _Tilia americana_ (basswood)
        - _Fraxinus americana_ (white ash)
    - Late hardwood
        - _Ostyra virginiana_ (hop-hornbeam)
    - Pine
        - _Pinus resinosa_ (red pine)

```{r param-table}
tbl <- readd(param_table)
tbl <- subset(tbl, select = -unit_parsed)
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
knitr::kable(tbl, escape = FALSE, caption = paste0(
  "**Table**: Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
))
```
